Funding programmes for early career researchers do not improve their independence

### 2024-01-19 article_formatted_doc.Rmd

  # word_document: default
  # # bookdown::pdf_document2: default
  # bookdown::html_document2: default
  #  df_print: paged
  #  number_sections: true
  # bookdown::word_document2: default
bibliography: merged.bib
csl: apa.csl
---
<!-- \doublespacing -->

@@

Your declaration of interest statement here.

@@

Name: David Janků 
Affiliation: 
[1] Institute of Sociological Studies, Faculty of Social Sciences, Charles University, Czech Republic
[2] Centre for Science, Technology, and Society Studies, Institute of Philosophy, Czech Academy of Sciences, Czech Republic  
Address: U Kříže 661/8, Praha 5 – Jinonice  
E-mail: david.janku@fsv.cuni.cz

@@

# Print the updated table
kable(df_summary, digits = 3, caption = "Counts and Proportions of Missing Data by Field") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

@@

kable(combined_table_before, 
      digits = 3, align = "c", booktabs = TRUE, caption = "Descriptives of All Groups Before Intervention") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 5, "Funded Control Group" = 5))

@@

kable(combined_table_after, 
      digits = 3, align = "c", booktabs = TRUE, caption = "Descriptives of All Groups After Intervention") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 5, "Funded Control Group" = 5))

@@

# Display the cleaned-up table with kable
kable(bal_df, "pipe", caption = "Summary of Covariate Balance Post-Matching For Unfunded Control Group") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

@@

# Display the cleaned-up table with kable
kable(bal_df_funded, "pipe", caption = "Summary of Covariate Balance Post-Matching For Funded Control Group") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

@@

kable(cor_matrix, format = "html", digits = 2, caption = "Correlation Matrix of RII indicator and its sub-parts") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

>>>>

  # word_document: default
  # # bookdown::pdf_document2: default
  # bookdown::html_document2: default
  #  df_print: paged
  #  number_sections: true
  # bookdown::word_document2: default
bibliography: merged.bib
csl: apa.csl
---

**Authors:**

David Janků  
[1] Institute of Sociological Studies, Faculty of Social Sciences, Charles University, Czech Republic; 
[2] Centre for Science, Technology, and Society Studies, Institute of Philosophy, Czech Academy of Sciences, Czech Republic

Radim Hladík  
[1] Centre for Science, Technology, and Society Studies, Institute of Philosophy, Czech Academy of Sciences, Czech Republic

@@

☐ The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

☒ The authors declare the following financial interests/personal relationships which may be considered as potential competing interests:

David Janku reports a relationship with Czech Science Foundation that includes: employment. If there are other authors, they declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

@@

Name: David Janků

Affiliation: 
[1] Institute of Sociological Studies, Faculty of Social Sciences, Charles University, Czech Republic
[2] Centre for Science, Technology, and Society Studies, Institute of Philosophy, Czech Academy of Sciences, Czech Republic  
Address: U Kříže 661/8, Praha 5 – Jinonice  
E-mail: david.janku@fsv.cuni.cz

@@

# Print the updated table
kable(df_summary, format = "markdown", digits = 3, caption = "Counts and Proportions of Missing Data by Field")

@@

kable(combined_table_before, 
      format = "markdown", digits = 3, align = "c", booktabs = TRUE, caption = "Descriptives of All Groups Before Intervention") 
  # kableExtra::add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 5, "Funded Control Group" = 5))

@@

kable(combined_table_after,
      format = "markdown", digits = 3, align = "c", booktabs = TRUE, caption = "Descriptives of All Groups After Intervention") %>%
  kableExtra::add_header_above(c(" " = 1, "Treatment Group" = 5, "Unfunded Control Group" = 5, "Funded Control Group" = 5))

# Assuming table_after_1, table_after_0, table_after_2 are your data frames for different groups
# 
# # Assuming each data frame has 5 columns
# header_columns = c("Header", rep("", 4))
# header_1 <- data.frame(matrix(nrow = 1, ncol = 5))
# colnames(header_1) <- header_columns
# header_1[1, 1] <- "Treatment Group"
# 
# header_0 <- data.frame(matrix(nrow = 1, ncol = 5))
# colnames(header_0) <- header_columns
# header_0[1, 1] <- "Unfunded Control Group"
# 
# header_2 <- data.frame(matrix(nrow = 1, ncol = 5))
# colnames(header_2) <- header_columns
# header_2[1, 1] <- "Funded Control Group"
# 
# header_names <- colnames(table_after_1)  # Assuming all tables have the same structure
# header_row <- setNames(data.frame(matrix(ncol = length(header_names), nrow = 1), stringsAsFactors = FALSE), header_names)
# header_row[1, 1] <- "Your Header Title"  # Set your header title in the first column
# 
# combined_table_after <- rbind(header_row, table_after_1, header_row, table_after_0, header_row, table_after_2)
# 
# 
# # # Assuming table_after_1, table_after_0, table_after_2 have the same column names
# # combined_table_after <- rbind(header_1, table_after_1, 
# #                               header_0, table_after_0, 
# #                               header_2, table_after_2)
# 
# # Now create the table in R Markdown
# knitr::kable(combined_table_after, format = "markdown", digits = 3,
#              caption = "Descriptives of All Groups After Intervention")

# # Table for Treatment Group 1
# table_after_1_md <- knitr::kable(table_after_1, format = "markdown", 
#                                  caption = "Treatment Group 1")
# 
# # Table for Unfunded Control Group
# table_after_0_md <- knitr::kable(table_after_0, format = "markdown", 
#                                  caption = "Unfunded Control Group")
# 
# # Table for Funded Control Group
# table_after_2_md <- knitr::kable(table_after_2, format = "markdown", 
#                                  caption = "Funded Control Group")
#

@@

# Display the cleaned-up table with kable
kable(bal_df, format = "markdown", caption = "Summary of Covariate Balance Post-Matching For Unfunded Control Group", digits = 3)

@@

# Display the cleaned-up table with kable
kable(bal_df_funded, format = "markdown", caption = "Summary of Covariate Balance Post-Matching For Funded Control Group", digits = 3)

@@

kable(cor_matrix, format = "markdown", digits = 2, caption = "Correlation Matrix of RII indicator and its sub-parts")
